Title?

### 2018-05-03 paper_wc.tex
Started set theoretical analysis.

% MECHANISM
\subsubsection{The PSP Mechanism}\label{mechanism}
The PSP auction as given in \cite{lazar} and \cite{semret} is designed for the
problem of network bandwidth allocation, and is analyzed as a noncooperative
game where $i\in\mcI$ agents buy the
fixed amount of bandwidth $d_i^j$ from sellers $j\in\mcI$.
The market price function (MPF) for a buyer-seller pair is,
% NEW MARKET PRICE
\begin{align}\label{dataprice}
\begin{split}
    P_i^j(z, s_{-i})= \inf\bigg\lbrace y\ge 0 : D_i^j(y, s_{-i}) \ge z \bigg\rbrace,\\
\end{split}
\end{align}
and is the of minimum prices a user bids in
order to obtain bandwidth $z$ given opponent profile $s_{-i}$. 
The maximum available quantity of data in auction
$j$ at unit price $y$ given $s_{-i}^j$ is,
% NEW INVERSE DEMAND
\begin{align}\label{datapriceinverse}
\begin{split}
    D_i^j(y, s_{-i}) &= \bigg[ D^j - \sum_{p_k^j>y,k\ne i} d_k^j  \bigg]^+,
\end{split}
\end{align}
where $D^j$ is the total amount of bandwith that user $j$ has to offer.
% DATA ALLOCATION RULE
For each $i \in \mcI$, the allocation from auction $j$ is,
% and so for profile $s_i$, for any $i \in \mcI$,
\begin{align}\label{dataallocation}
    a_i^j(s) &= \min\bigg( d_i^j, 
    D_i^j(p_i^j,s_{-i}^j)\bigg).
\end{align}
Finally, we have the cost of the allocation,
% DATA COST
\begin{align}\label{datacost}
    c_i^j(s) = \displaystyle\sum_{k\ne i} 
p_k^j \big[a_k^j(0; s_{-i}^j)
    -a_k^j(s_i^j;s_{-i}^j)\big].
\end{align}

It was shown, in \cite{lazar}, that the mechanism may converge to a Nash market
equilibria for differentiated services
allocated between multiple agents when all players bid their real marginal valuation
of the bandwidth resource. In other words, the PSP constraints are
sufficient to attain the desirable property of truthfullness through incentive
compatibility. The pricing mechanism upholds the \emph{exclusion-compensation
principle}, user $i$
pays for its allocation so as to exactly cover the ``social opportunity cost"
which is given by the declared willingness to pay (bids) of the users who are
excluded by $i$'s presence, and thus also compensates the seller for the maximum lost potential
revenue \cite{lazar}.
The PSP rules assume that an agent's valuation is represented by an elastic valuation function.
\definition{\cite{lazar}}
A real valued function, $\theta(\cdot): [0,\infty) \rightarrow [0,\infty)$, is an \emph{(elastic) valuation
function} on $[0, D]$ if 
\begin{itemize}
    \item $\theta(0) = 0$,
    \item $\theta$ is differentiable,
    \item ${\theta}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
${\theta}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta}'(z) \le
{\theta}'(\eta)
- \gamma(z - \eta)$. 
\end{itemize}
The function $\theta'(\cdot)$ on $[0, D]$ is called an (elastic) demand
function.
In the PSP market, a
user is considered truthful if their bid price equals their marginal valuation,
i.e. $p_i^j = {\theta_i^j}'$.

@@

We construct the model for a PSP data auction for mobile users
particpating in CMHK's secondary data-sharing market.
Define $\mcI = \lbrace 1, \cdots, I\rbrace$ as the set of users who purchase or sell
data from other users. We again define the bidding profile for any user to be 
$s \equiv
[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
, s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents. 
As a cellular network is fully connected, we assume that a buyer submits bids directly to sellers via the
cellular network. We assume that users are selfish, and therefore
rational. 
Users prefer to participate in the CMHK secondary market as it allows them to purchase
additional data for a cost less than the overage fee set by the ISP. 
Thus we assume that all users submit bids in order to maximize their
(private) valuation functions. 
In general, user preferences are defined by a utility function, $u$, which 
represents a users' valuation of an allocation minus the price.
Absent the cost or revenue from trading data, CMHK users gain utility from consuming
data. 
We assume that data is a unary resource belonging to the seller, and
therefore we identify each local auction with the identity of the seller
$j\in\mcI$.
We further show that user valuation satisfies the conditions for an
\emph{elastic demand function}, as in \cite{lazar}.
Finally, we assume in the CMHK market that a buyers' budget is always
sufficient, as the alternative is to pay the overage fee to the ISP.

@@

Our mechanism allows a buyer
to \emph{opt-out} of auctions by submitting zero bids. This strategy maximizes
utility while minimizing the number of positive bids submitted to the overall
market. We define an \textbf{opt-out function}, associated with a buyer $i$ as
part of its type. Buyer $i$, when determining how to aquire a possible allocation $a$,
will determine its bid quanities by,
\begin{equation}\label{opt-out}
    \g_i(a) = [\g_i^j(a)]_{j\in\mcI}.
\end{equation}
In a general sense, this abstraction applies our \emph{user strategy}
to the PSP rules.
% OPT-OUT BUYER
We define each buyer as a user $i\in\mcI$ with quasi-linear utility
function $u_i = [u_i^j]_{j\in\mcI}$, a buyers' utility function is of the form,
\begin{equation}\label{buyerutility}
    u_i = \theta_i \circ (\g_i(a)) - c_i,
\end{equation}
where the composition of the elastic valuation function $\theta_i$ with $e_i$ acts as a distribution function, splitting
the buyers' valuation of allocation $a$ across local markets (and thus multiple
sellers), and $\theta_i(\g_i(a)) - \g_i(\varrho)$ represents the buyers'
corresponding debit.  
In this way we extend the PSP rules described
in \cite{semret} to design equilibria across subsets of local data-exchange markets.

@@

Elastic valuation functions allow for even infinitesimal changes in the market
dynamics to be modeled. This, and the homogenous nature of data in the CMHK market, 
allows for the analysis of constraints imposed by the user strategies. 
Buyers may directly impact each other in local market intersections.
Thus our motivation to begin our analysis with buyer valuation $\theta_i$.
A buyers' valuation of an amount of data represents how much a buyer is willing
to pay for that amount. 
This is equivalent to the bid price, given a fixed amount of data,
satisfying $\theta_i$. We determine the
buyers' utility-maximizing bid given quantity $z\ge0$ to be a mapping to the lowest
possible unit price. We have,
% BUYER PRICING 
\begin{equation}\label{buyerinversedemand}
    f_i(z) \triangleq \inf\big\lbrace y\ge 0:
        \rho_i(y) \ge z, \ \forall \ j \in \mcI\big\rbrace,
\end{equation}
where $\rho_i(y)$ represents the demand function of buyer $i$ at bid price
$y\ge 0$, and gives the quantity that buyer $i$ would buy at a given price.
We determine that the market supply function is equivalent to buyer demand, and 
acts as an ``inverse" function of $f_i$. We have, for bid price $y\ge 0$,
% BUYER DEMAND 
\begin{equation}\label{datasupply}
    \rho_i(y) = \sum_{j\in\mcI : p_i^j\ge y} D^j.
\end{equation}
We note that $f_i$ is such that
$i$ could still bid in \emph{any} auction $j\in\mcI$.
Therefore, in a coordinated bid, the utility-maximizing bid price is the
lowest unit cost of the buyer to participate in all auctions, and corresponds to
the maximum reserve price amongst the sellers. 
%We will later show, in Proposition
%\ref{buyercoordinate}, that a buyer does not lose utility from coordinating its
%bids, i.e. using the same bid for all auctions.

@@

% MECHANISM
\subsubsection{Data Auction Mechanism}\label{datamechanism}
We now proceed to formally define the PSP auction, which determines the actions 
buyers and sellers in the CMHK market, and which we will denote the \emph{data}
PSP rules. The rules presented here incorporate of the opt-out function with the
mechanism as in \cite{lazar}, which we note greatly simplifies our
analysis. 
The market price function (MPF) for a buyer in the CMHK market
can be described as follows:
% NEW MARKET PRICE
\begin{align}\label{dataprice}
\begin{split}
    &\bar{P}_i(z, s_{-i}) =\displaystyle\sum_{j\in\mcI} \ \g_i^j \circ P_i^j(z_i^j,
s_{-i}^j) \\
    &= \sum_{j\in\mcI}\bigg(\inf\bigg\lbrace y\ge 0 : 
    {D_i^j}(y,s_{-i}^j) \ge \g_i^j(z) \bigg\rbrace \bigg),\\
\end{split}
\end{align}
and is interpreted as the aggragate of minimum prices that buyer $i$ bids in
order to obtain
data amount $z$ given opponent profile $s_{-i}$. We note that
the total minimum price for the buyer must be an aggragation of the
\emph{individual} prices of the buyers as it is possible that the reserve prices
of the individual sellers may vary.\\
\textbf{Remark:} We further note that except at points of discontinuity, from
Lemma \ref{uservaluation} we have that $P_i^j(z) = f_i(z)$. \\
%To simplify the notation, we define $z_i^j = d^j / \vs_i^j$ opt-out
%buyer $i$'s bid quantity. 
The maximum available quantity of data in auction
$j$ at unit price $y$ given $s_{-i}^j$ is: 
% NEW ALLOCATION RULE
\begin{align}
\begin{split}\label{datacomposed}
    \bar{D}_i^j(y,s_{-i}^j) &= \g_i^j \circ D_i^j( y,s_{-i}^j)\\
    &= \bigg\lbrack D^j - \sum_{p_k^j> y} \g_k^j(a)\bigg\rbrack^+.
\end{split}
\end{align}
% DATA ALLOCATION RULE
The resulting data allocation rule is a function of the local market
interactions between buyers and sellers over all local auctions, as is composed with $i$'s opt-out value, so that for each $i \in \mcI$, the
allocation from auction $j$ is,
% and so for profile $s_i$, for any $i \in \mcI$,
\begin{align}\label{dataallocation}
\begin{split}
    \bar{a}_i^j(&s) = \g_i^j \circ a_i^j(s) \\
    &= \min\bigg\lbrace \g_i^j(a), 
    \frac{\g_i^j(a)}{\displaystyle\sum_{p_k^j= p_i^j}\g_k^j(a)} 
D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace,
\end{split}
\end{align}
noting that for the full allocation from all auctions we may simply aggregate
over the seller pool.
Finally we must have that the cost to the buyer adheres to the second price
rule for each local auction, with total cost to buyer $i$,
% DATA COST
\begin{align}\label{datacost}
\begin{split}
    \bar{c}_i(s) &= \displaystyle\sum_{j\in\mcI} 
    p_i^j \bigg(\bar{a}_i^j(0; s_{-i}^j)
    -\bar{a}_i^j(s_i^j;s_{-i}^j)\bigg).
\end{split}
\end{align}
\textbf{Remark:} The cost to buyer $i$ adds up the willingness
of all buyers excluded by player $i$ to pay for quantity $\bar{a}_i^j$. i.e.
$$
    c_i^j(s) = \displaystyle\int_0^{\bar{a}_i^j} P_i^j(z, s_{-i}) \ dz.
$$
This is the ``social opportunity cost" of the PSP pricing rule.

@@

to be the buyer strategy with respect to quantity, and similarly for $\varrho$.

@@

Consider the set $\lambda^j$. For some buyer $i\in\mcI^j$, and then for
some seller $k \in \mcI_i$, we have a buyer $l \in \mcI^k$. By (\ref{jtoi}), $i,l \in \mcI^k$, and so the reserve price $p_*^k \le \min(p_l^*,
p_i^*)$, and $k, j\in \mcI_i\Rightarrow p_i^* \ge \max(p_*^k, p_*^j)$.
Suppose that $l \ni \mcI^j\Leftrightarrow j \ni \mcI_l$, so
that $p_l^* < p_*^j$, and
the valuation of buyer $l$ does not impact auction $j$ and vice versa, i.e. $\theta_l^j = 0$. Since $l\in\mcI^k$, $p_l^* \ge p_*^k\Rightarrow
p_*^k < p_*^j$, and $i\in\mcI^j \Rightarrow p_i^* \ge p_*^j$, so, $p_*^k \le
p_l^* < p_*^j \le p_i^*$, %<---- MAKE AN EQUATION?
for any buyer $l\in\lambda^j$ such that $l\ni \mcI^j$. Now, suppose $\exists \ l\in\mcI^k$ such that $l\in\mcI^j \Rightarrow p_l^* \ge
p_*^j$. In the case where $p_l^* > p_i^*$, we must have that 
$\exists \ q \in \mcI_l$ such that $p_*^q > p_*^k$, % \Rightarrow \theta_l^q > \theta_l^k$. 
which implies, again by (\ref{maxbid}), $q\ni\mcI_i \Leftrightarrow i
\ni\mcI^q \Rightarrow p_*^q >
p_i^*$, therefore $\theta_i^q = 0$, and the reserve price of auction $q$ does not effect the valuation of
buyer $i$, and as $p_*^k < p_*^j \le p_i^* < p_l^*$, we examine $\mcI^j$ using
(\ref{iff}).
Lastly, in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^g =
0$, for some $g\in\mcI_i$.
We have that for any $l\in\mcI^k$ such that $l\ni
\mcI^j$, $\theta_l^j =0$, and when $l\in \mcI^j$, then either $\theta_i^q =0$,
where $q\in\mcI_l$, or $\theta_l^g = 0$, where $g\in\mcI_i$, and as $p_*^k <
p_*^j \le p_l^* < p_i^*$, we examine $\mcI^k$ using (\ref{iff}),
a shift in $\mcI^k$ causes a shift in $\mcI_i$, so that $\exists \ g\in\mcI_i$
such that $p_*^g \ge p_*^j$. Thus, we
determine a direct influence as $l\in\mcI^k
\cap \Lambda^j$, such that $p_l^* > p_i^*$,
and an indirect influence as, for any $l\in\mcI^k
\setminus \Lambda^j$, where $p_l^* > p_i^*$ results in $i^*\in\mcI^j$ initiating a shift.

Now, consider the subset $\Lambda^j$, by
Proposition \ref{userunion}, a shift occurs in 2 cases. (1) If $i\in\mcI^j$
decreases its bid quantity so that $\sum_{i\in\mcI^j}
\g_i^j(a) < D^j$, and (2) if buyer $i^*$, defined in Proposition
\ref{sellerstrategy}, increases its valuation so that $p_{i^*}^j <
p_*^j$. First, let buyer $i\in\mcI^j$ be the buyer in auction $j$ with the lowest bid price,
and further suppose $p_i^* > p_*^j + \epsilon$. That is, $\exists \ q \in \mcI_i$ such
that $p_*^q > p_*^j$. Fixing all other bids, a decrease in $q$'s demand will
directly impact buyer $i$. If at the end of the bid iteration, we still have that $i$ is the
buyer with the lowest bid price, then (\ref{sellerinversedemand}) holds and $j$'s valuation does not change. Otherwise a new $i^*$ will be chosen upon
recomputing $\mcI^j$, as in Proposition \ref{buyerstrategy}, and the market
will attempt to regain equilibrium.
Clearly, if $i^*$ in case (1) or resulting from case (2) increases in valuation,
then $p_*^j$ will similarly increase, by (\ref{uservaluation}). Consider the 
seller $k^*\in\mcI_{i^*}$ at time $t$, and suppose that $p_*^{k^*} \ge p_*^j$, however, we have that $p_{i^*}^j <
p_*^j \Rightarrow i^* \ni \mcI^j \Rightarrow k^*\ni\Lambda^j\Rightarrow \mcI^{k^*} \ni
\lambda^j$. Now, consider a buyer $l^*\in\mcI^{k^*}$. We need only consider the
case where $\exists \ k \in\Lambda^j$ such that $l^*\in\mcI^k\subset \lambda^j$
where we determine the influence of $\Delta^{k^*}$ on $\Delta^j$ by (\ref{iff}).

@@

(z_i,y_i)$, where $\forall \ j \in \mcI_i$,

@@

    z_i^j &= \g_i^{j^*}(a), \\

@@

$d_i^{j^*}$ is the minimum quantity bid offered by any $j\in \mcI_i$,
so $d_i^{j^*} \le d_i^j, \ \forall \ j \in \mcI_i$. 

@@

    \g_i^k(a) \le z_i^j = \g_i^{j^*}(a) \le \g_i^{j}(a),

@@

    \g_i^{j^*}(a)  \le \bigg\lbrack D^{j} - \sum_{k\in \mcI^j : p_k^{j}> y_{i}^{j}} d_k^{j}\bigg\rbrack^+.

>>>>

% MECHANISM
\subsubsection{The PSP Mechanism}\label{mechanism}
The PSP auction as given in \cite{lazar} and \cite{semret} is designed for the
problem of network bandwidth allocation, and is analyzed as a noncooperative
game where $i\in\mcI$ agents buy the
fixed amount of bandwidth $d_i^j$ from sellers $j\in\mcI$.
The market price function (MPF) for a buyer-seller pair is,
% MARKET PRICE
\begin{align}\label{dataprice}
\begin{split}
    P_i^j(z, s_{-i})= \inf\bigg\lbrace y\ge 0 : D_i^j(y, s_{-i}) \ge z \bigg\rbrace,\\
\end{split}
\end{align}
and is the of minimum prices a user bids in
order to obtain bandwidth $z$ given opponent profile $s_{-i}$. 
The maximum available quantity of data in auction
$j$ at unit price $y$ given $s_{-i}^j$ is,
% INVERSE DEMAND
\begin{align}\label{datapriceinverse}
\begin{split}
    D_i^j(y, s_{-i}) &= \bigg[ D^j - \sum_{p_k^j>y,k\ne i} d_k^j  \bigg]^+,
\end{split}
\end{align}
where $D^j$ is the total amount of bandwith that user $j$ has to offer.
% DATA ALLOCATION RULE
For each $i \in \mcI$, the allocation from auction $j$ is,
% and so for profile $s_i$, for any $i \in \mcI$,
\begin{align}\label{dataallocation}
    a_i^j(s) &= \min\bigg( d_i^j, 
    D_i^j(p_i^j,s_{-i}^j)\bigg).
\end{align}
Finally, we have the cost of the allocation,
% DATA COST
\begin{align}\label{datacost}
    c_i^j(s) = \displaystyle\sum_{k\ne i} 
p_k^j \big[a_k^j(0; s_{-i}^j)
    -a_k^j(s_i^j;s_{-i}^j)\big].
\end{align}

It was shown, in \cite{lazar}, that the mechanism may converge to a Nash market
equilibria for differentiated services
allocated between multiple agents when all players bid their real marginal valuation
of the bandwidth resource. In other words, the PSP constraints are
sufficient to attain the desirable property of truthfullness through incentive
compatibility. The pricing mechanism upholds the \emph{exclusion-compensation
principle}, user $i$
pays for its allocation so as to exactly cover the ``social opportunity cost"
which is given by the declared willingness to pay (bids) of the users who are
excluded by $i$'s presence, and thus also compensates the seller for the maximum lost potential
revenue \cite{lazar}.
{
\definition{(Nash Equilibrium)}
A Nash equilibrium is defined as a strategy vector, or, in terms of PSP, a bid
profile $s$,
from which no player has a unilateral incentive to deviate (Johari, 2004)
(EXPAND?)
}\\

The PSP rules assume that an agent's valuation is represented by an elastic valuation function.
\definition{\cite{lazar}}
A real valued function, $\theta(\cdot): [0,\infty) \rightarrow [0,\infty)$, is an \emph{(elastic) valuation
function} on $[0, D]$ if 
\begin{itemize}
    \item $\theta(0) = 0$,
    \item $\theta$ is differentiable,
    \item ${\theta}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
${\theta}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta}'(z) \le
{\theta}'(\eta)
- \gamma(z - \eta)$. 
\end{itemize}
The function $\theta'(\cdot)$ on $[0, D]$ is called an (elastic) demand
function.
In the PSP market, a
user is considered truthful if their bid price equals their marginal valuation,
i.e. $p_i^j = {\theta_i^j}'$.

@@

We construct the model for a PSP data auction for mobile users
particpating in CMHK's secondary data-sharing market.
Define the index set $\mcI = \lbrace 1, \cdots, I\rbrace$ to represent the set of users who purchase or sell
data from other users. We again define the bidding profile for any user to be 
$s \equiv
[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
, s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents. 
Our strategy space is the vector space of all buyer $i$'s \emph{possible} bids,
$S_i=\Pi_{j\in\mcI} S_i^j$, and $S_{-i} =\Pi_{j\in\mcI} S_i^j(s_{-i})$ the
set of opponent profiles. We assume that the users are connected.
A buyer submits bids directly to sellers. Users prefer to participate in the CMHK secondary market as it allows them to purchase
additional data for a cost less than the overage fee set by the ISP. We assume
that users are selfish, and therefore rational. 
Thus we assume that all users submit bids in order to maximize their
(private) valuation functions. 
In general, user preferences are defined by a utility function, $u$, which 
represents a users' valuation of an allocation minus the price.
Absent the cost or revenue from trading data, CMHK users gain utility from consuming
data. 
We assume that data is a unary resource belonging to the seller, and
therefore we identify each local auction with the identity of the seller
$j\in\mcI$.
We further show that user valuation satisfies the conditions for an
\emph{elastic demand function}, as in \cite{lazar}.
Finally, we assume in the CMHK market that a buyers' budget is always
sufficient, as the alternative is to pay the overage fee to the ISP.

@@

Our mechanism allows a buyer
to \emph{opt-out} of auctions by submitting zero bids. This strategy maximizes
utility while minimizing the number of positive bids submitted to the overall
market. We define an \textbf{opt-out function}, associated with a buyer $i$ as
part of its type. Buyer $i$, when determining how to aquire a possible allocation $a$,
will determine its bid quanities by,
\begin{equation}\label{opt-out}
    \g_i(a) = [\g_i^j(a)]_{j\in\mcI}.
\end{equation}
In a general sense, this abstraction applies our \emph{user strategy}
to the PSP rules.
% OPT-OUT BUYER
We define each buyer as a user $i\in\mcI$ with quasi-linear utility
function $u_i = [u_i^j]_{j\in\mcI}$, a buyers' utility function is of the form,
\begin{equation}\label{buyerutility}
    u_i = \theta_i \circ (\g_i(a)) - c_i,
\end{equation}
where the composition of the elastic valuation function $\theta_i$ with $\g_i$
distributes a buyers' valuation of allocation $a$ across local markets (and thus
multiple sellers).
In this way we extend the PSP rules described
in \cite{semret} to design equilibria across subsets of local data-exchange markets.

@@

Elastic valuation functions allow for even infinitesimal changes in the market
dynamics to be modeled. This, and the homogenous nature of data in the CMHK market, 
allows for the analysis of constraints imposed by the user strategies. 
Buyers may directly impact each other in local market intersections.
Thus our motivation to begin our analysis with buyer valuation $\theta_i$.
A buyers' valuation of an amount of data represents how much a buyer is willing
to pay for that amount. 
This is equivalent to the bid price, given a fixed amount of data,
satisfying $\theta_i$. We determine the
buyers' utility-maximizing bid given quantity $z\ge0$ to be a mapping to the lowest
possible unit price. We have,
% BUYER PRICING 
\begin{equation}\label{buyerinversedemand}
    f_i(z) \triangleq \inf\big\lbrace y\ge 0:
        \rho_i(y) \ge z, \ \forall \ j \in \mcI\big\rbrace,
\end{equation}
where $\rho_i(y)$ represents the demand function of buyer $i$ at bid price
$y\ge 0$, and gives the quantity that buyer $i$ would buy at a given price.
We determine that the market supply function corresponds to an extreme of
possible buyer demand, and 
acts as an ``inverse" function of $f_i$. We have, for bid price $y\ge 0$,
% BUYER DEMAND 
\begin{equation}\label{datasupply}
    \rho_i(y) = \sum_{j\in\mcI : p_i^j\ge y} D^j.
\end{equation}
We note that $f_i$ is such that
$i$ could still bid in \emph{any} auction $j\in\mcI$.
Therefore, in a coordinated bid, the utility-maximizing bid price is the
lowest unit cost of the buyer to participate in all auctions, and corresponds to
the maximum reserve price amongst the sellers. 
%We will later show, in Proposition
%\ref{buyercoordinate}, that a buyer does not lose utility from coordinating its
%bids, i.e. using the same bid for all auctions.

@@

% MECHANISM
\subsubsection{Data Auction Mechanism}\label{datamechanism}
We now proceed to formally define the PSP auction, which determines the actions 
buyers and sellers in the CMHK market, and which we will denote the \emph{data}
PSP rules. The rules presented here incorporate of the opt-out function with the
mechanism as in \cite{lazar}, which we note greatly simplifies our
analysis. 
The market price function (MPF) for a buyer in the CMHK market
can be described as follows:
% NEW MARKET PRICE
\begin{align}\label{dataprice}
\begin{split}
    &\bar{P}_i(z, s_{-i}) =\displaystyle\sum_{j\in\mcI} \ \g_i^j \circ P_i^j(z_i^j,
s_{-i}^j) \\
    &= \sum_{j\in\mcI}\bigg(\inf\bigg\lbrace y\ge 0 : 
    {D_i^j}(y,s_{-i}^j) \ge \g_i^j(z) \bigg\rbrace \bigg),\\
and is interpreted as the aggragate of minimum prices that buyer $i$ bids in
order to obtain
data amount $z$ given opponent profile $s_{-i}$. We note that
the total minimum price for the buyer must be an aggragation of the
\emph{individual} prices of the buyers as it is possible that the reserve prices
of the individual sellers may vary.\\
\textbf{Remark:} We further note that except at points of discontinuity, from
Lemma \ref{uservaluation} we have that $P_i^j(z) = f_i(z)$. \\
(THE ABOVE IS GOOD, BUT DOESN'T FIT MY CONSTRUCTION, CHANGE TO BELOW?)
The market price function (MPF) for a buyer in the CMHK market
is determined per (\ref{buyerinversedemand}), and is defined as,
% NEW MARKET PRICE
\begin{align}\label{dataprice}
\begin{split}
    &\bar{P}_i(z, s_{-i}) =\displaystyle\sum_{j\in\mcI} \ \g_i^j \circ P_i^j(z_i^j,
s_{-i}^j) \\
    &= \sum_{j\in\mcI}\bigg(\inf\bigg\lbrace y\ge 0 : 
    {D_i^j}(y,s_{-i}^j) \ge \g_i^j(z), \ \forall \ j\in\mcI \bigg\rbrace \bigg),\\
and is interpreted as the price that buyer $i$ bids in
order to obtain
data amount $z$ given opponent profile $s_{-i}$.
The sellers pricing function is according to (\ref{sellerinversedemand}), 
\begin{align}\label{dataprice}
\begin{split}
    &\bar{P}^j(z, s_{-i}) =\displaystyle\sum_{i\in\mcI} \ \g_i^j \circ P_i^j(z_i^j,
s_{-i}^j) \\
    &= \sum_{j\in\mcI}\bigg(\sup\bigg\lbrace y\ge 0 : 
    {D_i^j}(y,s_{-i}^j) \ge \g_i^j(z), \ \forall \ i\in\mcI \bigg\rbrace \bigg).\\
We note that
the total price cannot be an aggragation of the
\emph{individual} bid prices as it is possible that the reserve prices
of the individual sellers may vary, which contradicts
(\ref{buyerinversedemand}) and (\ref{sellerinversedemand}).\\
\textbf{Remark:} We further note that except at points of discontinuity, from
Lemma \ref{uservaluation} we have that $P_i^j(z) = f_i(z)$. \\
%To simplify the notation, we define $z_i^j = d^j / \vs_i^j$ opt-out
%buyer $i$'s bid quantity. 
The maximum available quantity of data in auction
$j$ at unit price $y$ given $s_{-i}^j$ is: 
% NEW ALLOCATION RULE
\begin{split}\label{datacomposed}
    \bar{D}_i^j(y,s_{-i}^j) &= \g_i^j \circ D_i^j( y,s_{-i}^j)\\
    &= \bigg\lbrack D^j - \sum_{p_k^j> y} \g_k^j(a)\bigg\rbrack^+.
It follows from the upper-semicontinuity of $D_i^j$ that for $s_{-i}^j$ fixed, $\forall \ y,z \ge 0$,
\begin{equation}\label{dtop}
    \g_i^j(z) \le \g_i^j \circ D_i^j(y,s_{-i}^j) \Leftrightarrow y \ge \g_i^j
\circ P_i^j(z,s_{-i}^j).
% DATA ALLOCATION RULE
The resulting data allocation rule is a function of the local market
interactions between buyers and sellers over all local auctions, as is composed with $i$'s opt-out value, so that for each $i \in \mcI$, the
allocation from auction $j$ is,
% and so for profile $s_i$, for any $i \in \mcI$,
\begin{align}\label{dataallocation}
\begin{split}
    \bar{a}_i^j(&s) = \g_i^j \circ a_i^j(s) \\
    &= \min\bigg\lbrace \g_i^j(a), 
    \frac{\g_i^j(a)}{\displaystyle\sum_{p_k^j= p_i^j}\g_k^j(a)} 
D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace,
noting that for the full allocation from all auctions we may simply aggregate
over the seller pool.
Finally we must have that the cost to the buyer adheres to the second price
rule for each local auction, with total cost to buyer $i$,
% DATA COST
\begin{align}\label{datacost}
\begin{split}
    \bar{c}_i(s) &= \displaystyle\sum_{j\in\mcI} 
    p_i^j \bigg(\bar{a}_i^j(0; s_{-i}^j)
    -\bar{a}_i^j(s_i^j;s_{-i}^j)\bigg).
\textbf{Remark:} The cost to buyer $i$ adds up the willingness
of all buyers excluded by player $i$ to pay for quantity $\bar{a}_i^j$. i.e.
    c_i^j(s) = \displaystyle\int_0^{\bar{a}_i^j} P_i^j(z, s_{-i}) \ dz.
This is the ``social opportunity cost" of the PSP pricing rule.

@@

to be the buyer strategy with respect to quantity.

@@

Consider the set $\lambda^j$. For some buyer $i\in\mcI^j$, and then for
some seller $k \in \mcI_i$, we have a buyer $l \in \mcI^k$. By (\ref{jtoi}), $i,l \in \mcI^k$, and so the reserve price $p_*^k \le \min(p_l^*,
p_i^*)$, and $k, j\in \mcI_i\Rightarrow p_i^* \ge \max(p_*^k, p_*^j)$.
Suppose that $l \ni \mcI^j\Leftrightarrow j \ni \mcI_l$, so
that $p_l^* < p_*^j$, and
the valuation of buyer $l$ does not impact auction $j$ and vice versa, i.e. $\theta_l^j = 0$. Since $l\in\mcI^k$, $p_l^* \ge p_*^k\Rightarrow
p_*^k < p_*^j$, and $i\in\mcI^j \Rightarrow p_i^* \ge p_*^j$. Therefore, we
have that the ordering implied by (\ref{lambda}) and (\ref{llambda}) hold,
where,
\begin{equation}\label{ordering}
    p_*^k \le p_l^* < p_*^j \le p_i^*,
\end{equation} 
for any buyer $l\in\lambda^j$ such that $l\ni \mcI^j$. Now, suppose $\exists \ l\in\mcI^k$ such that $l\in\mcI^j \Rightarrow p_l^* \ge
p_*^j$. In the case where $p_l^* > p_i^*$, we must have that 
$\exists \ q \in \mcI_l$ such that $p_*^q > p_*^k$, % \Rightarrow \theta_l^q > \theta_l^k$. 
which implies, again by (\ref{maxbid}), $q\ni\mcI_i \Leftrightarrow i
\ni\mcI^q \Rightarrow p_*^q >
p_i^*$, therefore $\theta_i^q = 0$, and the reserve price of auction $q$ does not effect the valuation of
buyer $i$, and as $p_*^k < p_*^j \le p_i^* < p_l^*$, we examine $\mcI^j$ using
(\ref{iff}).
Lastly, in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^g =
0$, for some $g\in\mcI_i$.
We have that for any $l\in\mcI^k$ such that $l\ni
\mcI^j$, $\theta_l^j =0$, and when $l\in \mcI^j$, then either $\theta_i^q =0$,
where $q\in\mcI_l$, or $\theta_l^g = 0$, where $g\in\mcI_i$, and as $p_*^k <
p_*^j \le p_l^* < p_i^*$, we examine $\mcI^k$ using (\ref{iff}),
a shift in $\mcI^k$ causes a shift in $\mcI_i$, so that $\exists \ g\in\mcI_i$
such that $p_*^g \ge p_*^j$. Thus, we
determine a direct influence as $l\in\mcI^k
\cap \Lambda^j$, such that $p_l^* > p_i^*$,
and an indirect influence as, for any $l\in\mcI^k
\setminus \Lambda^j$, where $p_l^* > p_i^*$ results in $i^*\in\mcI^j$ initiating a shift.

Now, consider the subset $\Lambda^j$, by
Proposition \ref{userunion}, a shift occurs in 2 cases. (1) If $i\in\mcI^j$
decreases its bid quantity so that $\sum_{i\in\mcI^j}
\g_i^j(a) < D^j$, and (2) if buyer $i^*$, defined in Proposition
\ref{sellerstrategy}, increases its valuation so that $p_{i^*}^j <
p_*^j$. First, let buyer $i\in\mcI^j$ be the buyer in auction $j$ with the
lowest bid price, the ``lowest clearing player",
and further suppose $p_i^* > p_*^j + \epsilon$. That is, $\exists \ q \in \mcI_i$ such
that $p_*^q > p_*^j$. Fixing all other bids, a decrease in $q$'s demand will
directly impact buyer $i$. If at the end of the bid iteration, we still have that $i$ is the
buyer with the lowest bid price, then (\ref{sellerinversedemand}) holds and $j$'s valuation does not change. Otherwise a new $i^*$ will be chosen upon
recomputing $\mcI^j$, as in Proposition \ref{buyerstrategy}, and the market
will attempt to regain equilibrium.
Clearly, if $i^*$ in case (1) or resulting from case (2) increases in valuation,
then $p_*^j$ will similarly increase, by (\ref{uservaluation}). Consider the 
seller $k^*\in\mcI_{i^*}$ at time $t$, and suppose that $p_*^{k^*} \ge p_*^j$, however, we have that $p_{i^*}^j <
p_*^j \Rightarrow i^* \ni \mcI^j \Rightarrow k^*\ni\Lambda^j\Rightarrow \mcI^{k^*} \ni
\lambda^j$. Now, consider a buyer $l^*\in\mcI^{k^*}$. We need only consider the
case where $\exists \ k \in\Lambda^j$ such that $l^*\in\mcI^k\subset \lambda^j$
where we determine the influence of $\Delta^{k^*}$ on $\Delta^j$ by (\ref{iff}).

@@

\g_i \circ (z_i,y_i)$, where $\forall \ j \in \mcI_i$,

@@

    z_i^j &= \g_i^{j}(a), \\

@@

$d_i^{j^*}$ is the minimum quantity bid offered by any $j\in \mcI_i$.

@@

$k\ni\mcI_i$, $\g_i^k(a) \le z_i^j = \g_i^{j}(a)$,

@@

    \g_i^{j}(a)  \le \bigg\lbrack D^{j} - \sum_{k\in \mcI^j : p_k^{j}> y_{i}^{j}} d_k^{j}\bigg\rbrack^+.
